Compare pseqs

### 2019-05-17 comparepseqs.Rmd
Fixed adonis

     betadiversity <- mclapply(c2l(names(pseq)), function(x)
         list(min = calculateadonis(dset = meta(pseq[[x]]),
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.min,
                                    npermutations = 1000),
              full = calculateadonis(dset = meta(pseq[[x]]),
                                           matrix = bray.dist.matrix[[x]],
                                           covariates = covariates.full
                                           npermutations = 1000)
         mc.cores = length(pseq))
     saveRDS(betadiversity, file = "rds-comparepseqs/beta.diversity.rds")
    } else {
     betadiversity <- readRDS("rds-comparepseqs/beta.diversity.rds")
}
```

```{r plot alpha diversity, eval = FALSE}
beta.min <- lapply(c2l(names(pseq)), function(x) {
    alpha.min[[x]] %>% mutate(R2 = 0) %>% select(model_name, R2, response)
})

@@

alpha.plot.min <- mclapply(alpha.min, function(x) { mergediversities(x, 
                               },
                               ## plot.alpha(x %>%
                               ##                    mutate(Name = term,
                               ##                           R2 = 0,
                               ##                           Qstar = ifelse(p.value < 0.05, '*', ' ')),
                               ##                    colorlimit = 0.6),
                           mc.cores = length(pseq))

>>>>

    betadiversity <- mclapply(c2l(names(pseq)), function(x)
        list(min = calculateadonis(dset = meta(pseq[[x]]),
                                   matrix = bray.dist.matrix[[x]],
                                   covariates = covariates.min,
                                   npermutations = 1),
             full = calculateadonis(dset = meta(pseq[[x]]),
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.full,
                                    npermutations = 1)),
        mc.cores = length(pseq))

     saveRDS(betadiversity, file = "rds-comparepseqs/beta.diversity.rds")
    } else {
     betadiversity <- readRDS("rds-comparepseqs/beta.diversity.rds")
}
```

```{r plot alpha diversity, eval = FALSE}

str(betadiversity)

a <- mergediversities(alphadiversity[["ncbi"]], betadiversity[["ncbi"]])

alphadiversity[["ncbi"]]
betadiversity[["ncbi"]]

names(betadiversity)
betadiversity[[""]]

 alpha.select <- alphadiversity[["R16S"]][["min"]] %>% select(estimate, p.value, response)

beta.rbind <- betadiversity[["R16S"]][["min"]] %>%
    data.table::rbindlist(id = "model_name")

%>%
            dplyr::filter(term %in% responses) %>%
            dplyr::select(response, R2)

        merge( alpha.select , beta.rbind, by = "response") %>%
            merge(names.dset %>% select(Covariate, Category, Name), by.x ="response", by.y = "Covariate") %>%
            mutate(Qstar = ifelse(p.value < 0.05, '*', ' '))
    })

vectortolist(names(alphadiversity[["R16S"]]))

c2l(names(pseq))
beta.min <- lapply(c2l(names(pseq)), function(x) {
    mergediversities(alphadiversity[[x]], betadiversity[[x]])
})

@@

alpha.plot.min <- mclapply(alpha.min, function(x) { mergediversities(},
                               mc.cores = length(pseq))
